### 2019-01-14 journal/experiments.tex
add new graph

In order to check our results statistically, we sliced the FPF benchmark tests into 20 randomly selected equal-sized (as much as possible) distinct subsets.  The repair metric had a mean APFD (89.23\%) for these subsets that was 2.85\% better than the mean APFD for the best benchmark metric (86.76\%), over sets of $\sim 10$ faults. The result was statistically significant ($p < 0.05$ by Wilcoxon test).   Median repair APFD was 90.05\%, vs. 84.75\% for the best benchmark metric.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.8\columnwidth]{comparejs}
  \caption{APFD values for Spidermonkey suite slices}
  \label{comparejs}
\end{figure}%

In order to check our results statistically, we sliced the FPF benchmark tests into 20 randomly selected equal-sized (as much as possible) distinct subsets (Figure \ref{comparejs}) .  The repair metric had a mean APFD (89.23\%) for these subsets that was 2.85\% better than the mean APFD for the best benchmark metric (86.76\%), over sets of $\sim 10$ faults. The result was statistically significant ($p < 0.05$ by Wilcoxon test).   Median repair APFD was 90.05\%, vs. 84.75\% for the best benchmark metric.
